Hippocampal replay of experience at slow speeds

### 2021-04-30 Article.tex
Update on Overleaf.

@@

Finally, one important question is how our method compares to the standard decoder. We would like to emphasize, as we have stated in the introduction, that this comparison is complicated due to the variety of parameters and inference methods used and referred to as the standard "Bayesian" decoder.

>>>>

% Figure 6
\begin{figure}
\includegraphics[width=0.80\linewidth]{figures/Figure6/Figure6_v2}
\caption{
Comparison of the state space decoder to the standard "Bayesian" decoder. \textbf{(A)} Radon transform  \textbf{(B)} MAP estimate  \textbf{(C)} Linear regression  \textbf{(D)} State space decoder
}
\label{fig:6}

@@

% Table 1
\begin{wraptable}{l}{0.5\textwidth}{
\begin{tabular}{lll}
\textbf{Dynamic}                       & \textbf{\begin{tabular}[c]{@{}l@{}}Percent.\\ Sig.\end{tabular}} & \textbf{Number Sig.}               \\ \hline
\multicolumn{1}{|l|}{Stat.}            & \multicolumn{1}{l|}{8\%}                                         & \multicolumn{1}{l|}{542 of 7176}   \\ \hline
\multicolumn{1}{|l|}{Stat.-Cont.-Mix.} & \multicolumn{1}{l|}{14\%}                                        & \multicolumn{1}{l|}{2253 of 16106} \\ \hline
\multicolumn{1}{|l|}{Cont.}            & \multicolumn{1}{l|}{30\%}                                        & \multicolumn{1}{l|}{1368 of 4511}  \\ \hline
\multicolumn{1}{|l|}{Cont.-Frag.-Mix.} & \multicolumn{1}{l|}{31\%}                                        & \multicolumn{1}{l|}{799 of 2562}   \\ \hline
\multicolumn{1}{|l|}{Frag.}            & \multicolumn{1}{l|}{15\%}                                        & \multicolumn{1}{l|}{244 of 1598}   \\ \hline
\end{tabular}
}
  \caption{Number of significant SWRs that contain each dynamic. SWRs were fit using the random transform with 1000 shuffles of the posterior in each time bin.}\label{tab:supp1}
\end{wraptable}

Finally, an important question is how our method compares to the standard "Bayesian" decoder. This comparison is complicated due to the variety of parameters and inference methods used and referred to as the standard "Bayesian" decoder. For the sake of comparison, we used clusterless decoding in 20 ms time bins and used three common methods of inferring the trajectory: the radon transform \citep{DavidsonHippocampalReplayExtended2009, FarooqEmergencepreconfiguredplastic2019}, linear regression \citep{KarlssonAwakereplayremote2009, CarrHippocampalreplayawake2011, ShinDynamicsAwakeHippocampalPrefrontal2019}, and the MAP estimate (the maximum probability position of each time bin) \citep{PfeifferAutoassociativedynamicsgeneration2015, StellaHippocampalReactivationRandom2019, KaeferReplayBehavioralSequences2020}. We then compared how the estimated trajectory speeds varied by dynamic for each method. This reveals two key insights. First, the choice of method can give very different estimated speeds distributions for the SWRs. In particular, the methods that rely on fitting a line for the entire SWR (the radon transform and the linear regression), tend to estimate that the SWRs proceed at faster speeds.
